The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-03 manuscript/manuscript.Rnw
use horizontal and vertical axis

print(ggplot(cpt.distribution.shape[`Expression (FPKM)` > 1,],
             aes(x=`Expression (FPKM)`,color=`Lowest Expression`,y=num_genes))
      + geom_line(lwd=1)
      + xlab(expression(FPKM))
      + ylab("Genes with N-th Lowest Expression")
      + scale_y_log10()
      + scale_x_log10()
      + geom_vline(xintercept=10)
      + geom_segment(mapping=aes(y=V1,
                         yend=V1,
                         xend=10,
                         x=100,
                         color=`Lowest Expression`),
                     data=cpt.distribution.shape[`Expression (FPKM)` > 10,
                                              max(num_genes),`Lowest Expression`],
                     arrow=arrow(length=unit(0.5,"cm"))
                   )
      + geom_text(mapping=aes(x=100,
                      y=V1,
                      label=paste0(V1," genes"),override=TRUE),
                  data=cpt.distribution.shape[`Expression (FPKM)` > 10,
                      max(num_genes),`Lowest Expression`],
                  show_guide=FALSE,
                  hjust=0
                  )
      + guides(color=guide_legend(title="Lowest\nExpression"))
      )
@ 
\caption{Distribution shape of placenta core genes. The Y axis shows
  the number of orthologous gene sets included in the core placenta
  transcriptome if the least expression cutoff (or second-least, etc.)
  was set to the X axis. For example, if the cutoff is set to 10
  (vertical black line), 37 genes would be included if the FPKM of all
  species must be at least 10, 134 genes would be included if all but
  one species must have FPKM of at least 10. 655 genes would be
  included if all but five species must have FPKM of at least 10.}
\label{fig:core_placenta_transcriptome_shape}
\end{figure}

>>>>

print(ggplot(cpt.distribution.shape[`Expression (FPKM)` > 1,],
             aes(x=`Expression (FPKM)`,color=`Lowest Expression`,y=num_genes))
      + geom_line(lwd=1)
      + xlab(expression(FPKM))
      + ylab("Genes with N-th Lowest Expression")
      + scale_y_log10()
      + scale_x_log10()
      + geom_vline(xintercept=10)
      + geom_segment(mapping=aes(y=V1,
                         yend=V1,
                         xend=10,
                         x=100,
                         color=`Lowest Expression`),
                     data=cpt.distribution.shape[`Expression (FPKM)` > 10,
                                              max(num_genes),`Lowest Expression`],
                     arrow=arrow(length=unit(0.5,"cm"))
                   )
      + geom_text(mapping=aes(x=100,
                      y=V1,
                      label=paste0(V1," genes"),override=TRUE),
                  data=cpt.distribution.shape[`Expression (FPKM)` > 10,
                      max(num_genes),`Lowest Expression`],
                  show_guide=FALSE,
                  hjust=0
                  )
      + guides(color=guide_legend(title="Lowest\nExpression"))
      )
@ 
\caption{Distribution shape of placenta core genes. The vertical axis shows
  the number of orthologous gene sets included in the core placenta
  transcriptome if the least expression cutoff (or second-least, etc.)
  was set to the horizontal axis. For example, if the cutoff is set to 10
  (vertical black line), 37 genes would be included if the FPKM of all
  species must be at least 10, 134 genes would be included if all but
  one species must have FPKM of at least 10. 655 genes would be
  included if all but five species must have FPKM of at least 10.}
\label{fig:core_placenta_transcriptome_shape}
\end{figure}
